---
title: "tables_for_scare_quotes"
author: "Drew Walker"
date: "12/14/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(table1)
library(tidytext)
library(tm)
```

```{r, load-data}
labeled_heldout <- read_csv("labeled_heldout.csv")

test_set <- read_csv("gold_standard_bias_annotation_doc_training_1200.csv")
```
# By Patient Summary DFs

This will show the breakdown of quoted counts, number of charts, providers, admissions by patient in both held out and test sets 
```{r patients-dfs}

# Number of quoted sentences
test_by_subject_id <- test_set %>% 
  group_by(SUBJECT_ID) %>% 
  summarize(quote_count = n())

heldout_by_subject_id <- labeled_heldout %>% 
  group_by(SUBJECT_ID) %>% 
  summarize(quote_count = n())
# Number of charts
test_charts <-test_set %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(ROW_ID_x) %>% 
  summarize(chart_count = n())

heldout_charts <-labeled_heldout %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(ROW_ID_x) %>% 
  summarize(chart_count = n())

# Number of admissions
test_adm <-test_set %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(HADM_ID) %>% 
  summarize(admission_count = n())

heldout_adm <-labeled_heldout %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(HADM_ID) %>% 
  summarize(admission_count = n())

# Number of providers writing quotes 

# Number of admissions
test_providers <-test_set %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(CGID) %>% 
  summarize(provider_count = n())

heldout_providers <-labeled_heldout %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(CGID) %>% 
  summarize(provider_count = n())

# Merge dataframes by patient 

test_quotes_patient_df <- plyr::join_all(list(test_by_subject_id,test_charts,test_adm,test_providers), by='SUBJECT_ID', type='left') 

heldout_quotes_patient_df <- plyr::join_all(list(heldout_by_subject_id,heldout_charts,heldout_adm,heldout_providers), by='SUBJECT_ID', type='left') 


# Test table 1 
table1(~quote_count + chart_count + admission_count+provider_count, data= test_quotes_patient_df)

# Heldout table 1

table1(~quote_count + chart_count + admission_count+provider_count, data= heldout_quotes_patient_df)


```
# Summary Label DF Frequencies
These summary tables show how many different quotes found, charts, providers, and admissions per each quote type
```{r categories-df}
labeled_heldout$predicted_label <- as.factor(labeled_heldout$predicted_label)
#Number of quoted sentences
test_by_label <- test_set %>% 
  group_by(quote_use) %>% 
  summarize(quote_count = n())

heldout_by_label <- labeled_heldout %>% 
  group_by(predicted_label) %>% 
  summarize(quote_count = n()) 
# Number of charts
test_charts_label <-test_set %>% 
  group_by(quote_use) %>% 
  distinct(ROW_ID_x) %>% 
  summarize(chart_count = n())

heldout_charts_label <-labeled_heldout %>% 
  group_by(predicted_label) %>% 
  distinct(ROW_ID_x) %>% 
  summarize(chart_count = n())


# Number of providers
test_providers_label <-test_set %>% 
  group_by(quote_use) %>% 
  distinct(CGID) %>% 
  summarize(provider_count = n())

heldout_providers_label <-labeled_heldout %>% 
  group_by(predicted_label) %>% 
  distinct(CGID) %>% 
  summarize(provider_count = n())

heldout_adm_label <-labeled_heldout %>% 
  group_by(predicted_label) %>% 
  distinct(HADM_ID) %>% 
  summarize(admission_count = n())

test_adm_label <-test_set %>% 
  group_by(quote_use) %>% 
  distinct(HADM_ID) %>% 
  summarize(admission_count = n())
# Merge dataframes by patient 

test_label_df <- plyr::join_all(list(test_by_label,test_charts_label,test_providers_label,test_adm_label), by='quote_use', type='left') 



heldout_quotes_patient_df <- plyr::join_all(list(heldout_by_label,heldout_charts_label,heldout_providers_label,heldout_adm_label), by='predicted_label', type='left') 


# Test table 1 
table1(~quote_count + chart_count + admission_count+provider_count|quote_use, data= test_label_df)

# Heldout table 1

table1(~quote_count + chart_count + admission_count+provider_count|predicted_label, data= heldout_quotes_patient_df)



```



# ICC Data Prep
# By Patients 

## Test Set 
```{r test-counts-patients}
test_quote_use_df_table <- test_set %>% 
  mutate(quote_label = case_when(quote_use == 0 ~"Helpful",
                   quote_use == 1 ~"Harmful",
                   quote_use == 2 ~"Possibly_Harmful",
                   quote_use == 3 ~"Not_Applicable")) %>% 
  pivot_wider(names_from = quote_label,values_from = quote_label,
           values_fn = function(x) sum(!is.na(x)), values_fill = 0)
```


## Labeled Set 
```{r labeled-counts-patients}
labeled_quote_use_df_table <- labeled_heldout %>% 
  mutate(quote_label = case_when(predicted_label == 0 ~"Helpful",
                   predicted_label == 1 ~"Harmful",
                   predicted_label == 2 ~"Possibly_Harmful",
                   predicted_label == 3 ~"Not_Applicable")) %>% 
  pivot_wider(names_from = quote_label,values_from = quote_label,
           values_fn = function(x) sum(!is.na(x)), values_fill = 0)

```

# QUotes by type of note
```{r category-table-ones}
table1(~predicted_label|CATEGORY, data= labeled_quote_use_df_table)

test_quote_use_df_table$quote_use <- as.factor(test_quote_use_df_table$quote_use)
table1(~quote_use|CATEGORY, data= test_quote_use_df_table)
```
# ICC for patients and providers and note types
https://cran.r-project.org/web/packages/iccCounts/index.html
# Labeled data
```{r labeled-count-icc}
# Labeled
labeled_quote_use_df_table <- labeled_quote_use_df_table %>% 
  ungroup()
#Harmful scores
iccCounts::icc_counts(labeled_quote_use_df_table,y='Harmful',id='CATEGORY')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Harmful',id='SUBJECT_ID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Harmful',id='CGID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Harmful',id='GENDER')
#Helpful scores
iccCounts::icc_counts(labeled_quote_use_df_table,y='Helpful',id='CATEGORY')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Helpful',id='SUBJECT_ID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Helpful',id='CGID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Helpful',id='GENDER')

# Possibly harmful
iccCounts::icc_counts(labeled_quote_use_df_table,y='Possibly_Harmful',id='CATEGORY')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Possibly_Harmful',id='SUBJECT_ID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Possibly_Harmful',id='CGID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Helpful',id='GENDER')
# NA 
iccCounts::icc_counts(labeled_quote_use_df_table,y='Not_Applicable',id='CATEGORY')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Not_Applicable',id='SUBJECT_ID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Not_Applicable',id='CGID')
iccCounts::icc_counts(labeled_quote_use_df_table,y='Not_Applicable',id='GENDER')

```

# Test data
```{r count-icc-test}
# Labeled
test_quote_use_df_table <- test_quote_use_df_table %>% 
  ungroup()
#Harmful scores
iccCounts::icc_counts(test_quote_use_df_table,y='Harmful',id='CATEGORY')
iccCounts::icc_counts(test_quote_use_df_table,y='Harmful',id='SUBJECT_ID')
iccCounts::icc_counts(test_quote_use_df_table,y='Harmful',id='CGID')

iccCounts::icc_counts(test_quote_use_df_table,y='Harmful',id='GENDER')
#Helpful scores
iccCounts::icc_counts(test_quote_use_df_table,y='Helpful',id='CATEGORY')
iccCounts::icc_counts(test_quote_use_df_table,y='Helpful',id='SUBJECT_ID')
iccCounts::icc_counts(test_quote_use_df_table,y='Helpful',id='CGID')
iccCounts::icc_counts(test_quote_use_df_table,y='Helpful',id='GENDER')
# Possibly harmful
iccCounts::icc_counts(test_quote_use_df_table,y='Possibly_Harmful',id='CATEGORY')
iccCounts::icc_counts(test_quote_use_df_table,y='Possibly_Harmful',id='SUBJECT_ID')
iccCounts::icc_counts(test_quote_use_df_table,y='Possibly_Harmful',id='CGID')
iccCounts::icc_counts(test_quote_use_df_table,y='Possibly_Harmful',id='GENDER')
# NA 
iccCounts::icc_counts(test_quote_use_df_table,y='Not_Applicable',id='CATEGORY')
iccCounts::icc_counts(test_quote_use_df_table,y='Not_Applicable',id='SUBJECT_ID')
iccCounts::icc_counts(test_quote_use_df_table,y='Not_Applicable',id='CGID')
iccCounts::icc_counts(test_quote_use_df_table,y='Not_Applicable',id='GENDER')
```

```{r, gender-harmful-regression}
gender_harmful_model <- glm(Harmful~GENDER, data = test_quote_use_df_table)

confint(gender_harmful_model)

summary(gender_harmful_model)

gender_helpful_model <- glm(Helpful~GENDER, data = test_quote_use_df_table)

confint(gender_helpful_model)

summary(gender_helpful_model)

gender_possibly_model <- glm(Possibly_Harmful~GENDER, data = test_quote_use_df_table)

confint(gender_possibly_model)

summary(gender_possibly_model)

gender_na_model <- glm(Not_Applicable~GENDER, data = test_quote_use_df_table)

confint(gender_na_model)

summary(gender_na_model)

```

```{r patient-gender-sample}
gender_test <- test_set %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(SUBJECT_ID,GENDER)
table(gender_test$GENDER)

gender_labeled <- labeled_heldout %>% 
  group_by(SUBJECT_ID) %>% 
  distinct(SUBJECT_ID,GENDER)
table(gender_labeled$GENDER)


table1(~GENDER,data=gender_test)

table1(~GENDER,data=gender_labeled)
```
# labeled descriptions
```{r,desc-labeled}
table(labeled_heldout$CATEGORY)
labeled_heldout$CGID <- as.factor(labeled_heldout$CGID)
labeled_heldout %>% 
  distinct(CGID)
labeled_heldout %>% 
  distinct(SUBJECT_ID)

labeled_heldout %>% 
  distinct(HADM_ID)
labeled_heldout %>% 
  distinct(ROW_ID_x)
```
# Test descriptions
```{r,desc-test}
table(test_set$CATEGORY)
test_set$CGID <- as.factor(test_set$CGID)
test_set %>% 
  distinct(CGID)
test_set %>% 
  distinct(SUBJECT_ID)

test_set %>% 
  distinct(HADM_ID)
test_set %>% 
  distinct(ROW_ID_x)
```

